%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} \\
      \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Truong Pham}} & Email : \href{mailto:truongptk30a3@gmail.com}{truongptk30a3@gmail.com}\\
  \href{https://gravieb.wordpress.com/}{https://gravieb.wordpress.com} & Mobile : +84-906-022-0187 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Phan Boi Chau Specialized High School, Nghe An - Viet Nam}{09/2001 - 06/2004}
      {2rd prize Vietnam National Physics Contest for high school - 2004}
      {Bronze medal 5th Asian Physics Olympiad - 2004}
    \resumeSubheading
      {Hanoi University of Science and Technology}{09/2004 - 06/2009}
      {Bachelor of Automatic Control/Engineering in Electrical and Electronics;  GPA: 8.15/10}
      {Graduation thesis: Design 48V DC - 220V AC, 500W Converter}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Employment && Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {VTI Co Limited}{Tokyo, Japan}
      {Embedded Software Engineer}{8/2018 - Present}
      \resumeItemListStart
        \resumeItem{3D TOF sensor}
          {Development framework and driver of 3D TOF sensor on Android}{8/2018 - Present}
      \resumeItemListEnd

    \resumeSubheading
      {FPT Japan}{Tokyo, Japan}
  %    {Bridge System Engineer}{04/2017 - 07/2018}
      {Embedded Software Engineer}{07/2013 - 04/2017}
      \resumeItemListStart
        \resumeItem{Linux Kernel BSP}
          {Investigate issue when upgrading Linux kernel 3.18.24 to 3.18.82 on SOC of customer.}{5/2018 - 7/2018}
        \resumeItem{eT-Kenel BSP}
          {Porting (design, coding, testing) HD-DMAC, HS-SPI, I2S, ENC/DEC driver on eTKernel to new SOC of customer.}
      \resumeItemListEnd

    \resumeSubheading
      {FPT Software Ha Noi}{HaNoi, VietNam}
      {Embedded Software Developer}{07/2009 - 07/2013}
      \resumeItemListStart
        \resumeItem{Audio Video Decoder}
          {Develop firmware of digital television (Digital Video Broadcasting - Terrestrial).}
        \resumeItem{QuantDesk}
          {Python backend for a web application used by hedge fund managers for portfolio management.}
      \resumeItemListEnd

    \resumeSubheading
      {Binh Anh Electronics}{HaNoi, VietNam}
      {Embedded Software Developer}{11/2007-02/2009}
      \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning}
          {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the python library QSTK.}
        \resumeItem{Teaching Assistant - Computational Investing}
          {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Other activity}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
